---
title: "simulation"
author: "Yingyu Cui"
date: "2024-11-06"
output: github_document
---

```{r setup }
library(tidyverse)

set.seed(1)
```

# first write a function
```{r function}
sim_mean_sd = function(n, mu = 2, sigma = 3) {
  
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma),
  )
  
  sim_data |> 
    summarize(
      mu_hat = mean(x),
      sigma_hat = sd(x)
    )
}
```
and run a for loop
```{r for loop}
output = vector("list", 100)

for (i in 1:100) {
  output[[i]] = sim_mean_sd(30)
}

sim_results = bind_rows(output)
```

# bind_rows(output) could transfer the format of list in output into data frame

or we could use
```{r or}
rerun(100, sim_mean_sd(30)) |> 
  bind_rows()

#now has been changed into
map(1:100, ~sim_mean_sd(30)) |> 
  bind_rows()

# for more convenience, we could use this to save function writing
sim_results_df =   
  map(1:100, \(i) sim_mean_sd(30, 2, 3)) |> 
  bind_rows()
```

another way to do this 
```{r another}
sim_results_df = 
  expand_grid(
    sample_size = 30,
    iter = 1:100
  ) |> 
  mutate(
    estimate_df = map(sample_size, sim_mean_sd)
  ) |> 
  unnest(estimate_df)

# which is still a good way
```

analyze the result 
```{r analyze} 
sim_results_df |> 
  ggplot(aes(x = mu_hat)) + 
  geom_density()

sim_results_df |> 
  pivot_longer(
    mu_hat:sigma_hat,
    names_to = "parameter", 
    values_to = "estimate") |> 
  group_by(parameter) |> 
  summarize(
    emp_mean = mean(estimate),
    emp_sd = sd(estimate)) |> 
  knitr::kable(digits = 3)
# analyze the two plots 
```

# here we test for mean and sd for several ns
```{r several n}
sim_results_df = 
  expand_grid(
    sample_size = c(30, 60, 120, 240),
    iter = 1:1000
  ) |> 
  mutate(
    estimate_df = map(sample_size, sim_mean_sd)
  ) |> 
  unnest(estimate_df)

# str_c add some words in front of something
# fct_inorder is to sort the factor in the order of the variables you choose

# violin plot and boxplot transfer
```

analyze of the results 
```{r analyze2} 
sim_results_df |> 
  mutate(
    sample_size = str_c("n = ", sample_size),
    sample_size = fct_inorder(sample_size)) |> 
  ggplot(aes(x = sample_size, y = mu_hat, fill = sample_size)) + 
  geom_violin()
```

```{r calculation }
sim_results_df |> 
  pivot_longer(
    mu_hat:sigma_hat,
    names_to = "parameter", 
    values_to = "estimate") |> 
  group_by(parameter, sample_size) |> 
  summarize(
    emp_mean = mean(estimate),
    emp_var = var(estimate)) |> 
  knitr::kable(digits = 3)
```

# SLR for n
```{r SLR}
sim_regression = function(n, beta0 = 2, beta1 = 3) {
  
  sim_data = 
    tibble(
      x = rnorm(n, mean = 1, sd = 1),
      y = beta0 + beta1 * x + rnorm(n, 0, 1)
    )
  
  ls_fit = lm(y ~ x, data = sim_data)
  
  tibble(
    beta0_hat = coef(ls_fit)[1],
    beta1_hat = coef(ls_fit)[2]
  )
}
```

```{r test}
sim_results_df = 
  expand_grid(
    sample_size = 30,
    iter = 1:500
  ) |> 
  mutate(
    estimate_df = map(sample_size, sim_regression)
  ) |> 
  unnest(estimate_df)
```

```{r plot}
sim_results_df |> 
  ggplot(aes(x = beta0_hat, y = beta1_hat)) + 
  geom_point()
```

# vary two simulation parameter 
```{r vary} 
sim_results_df = 
  expand_grid(
    sample_size = c(30, 60, 120, 240),
    true_sd = c(6, 3),
    iter = 1:1000
  ) |> 
  mutate(
    estimate_df = 
      map2(sample_size, true_sd, \(n, sd) sim_mean_sd(n = n, sigma = sd))
  ) |> 
  unnest(estimate_df)
```

```{r analyze3}
sim_results_df |> 
  mutate(
    true_sd = str_c("True SD: ", true_sd),
    true_sd = fct_inorder(true_sd),
    sample_size = str_c("n = ", sample_size),
    sample_size = fct_inorder(sample_size)) |> 
  ggplot(aes(x = sample_size, y = mu_hat, fill = sample_size)) + 
  geom_violin() + 
  facet_grid(. ~ true_sd)
```

# cache in {r, cache = TRUE}, could save the huge result you made, but not that useful ?
# set.seed() could make the result reproducible